Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-18 content/impl.tex
inter- and intra-procedural to interprocedural and intraprocedural
edit efficiency subsection

For paths $p$ that start with the entry point~$\startmain$,
\begin{equation}\label{eq:envTransToEdgefn}
  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
\end{equation}
where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all inter-procedurally realizable paths.

@@

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
and that he defined $\backEq$ related to the equivalence transformation.}
\otodo{I don't understand this comment. What does it mean?}

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
  \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)\neq\top_T\}.
\end{equation}

@@

\subsection{Efficiency}
\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
    receivers is a constant independent of the size of the program. That seems a stretch. If
    it's linear in the size of the program, then we would need to add a factor to their complexity
    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
As defined in~Sagiv et al.~\cite{sagiv1996precise}, a representation of micro functions is efficient if the following conditions hold:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient.
\end{restatable}

@@

>>>>

For paths $p$ that start with the entry point~$\startmain$,
\begin{equation}\label{eq:envTransToEdgefn}
  \menv(p)(\Omega)(d)=\bigsqcap_{r\in\mathsf{RP}(p,\,d)}\edgefn(r)(\top)\,,
\end{equation}
where $n\in N^*$, $d\in D$, $p\in\ivp(n)$, and $\mathsf{RP}$ is the set of all interprocedurally realizable paths.

@@

Recall that in the equivalence transformation lattice $L^\equiv$, $\bot$ means reachable
and $\top$ means unreachable.
Therefore, a result $\rho=\resultIDE(\transEq(P))$ of the equivalence IDE analysis
is converted to an IFDS result as follows:
\begin{equation}\label{eq:transEqDef}
  \backEq(\rho) = \lambda n.\{d\mid\rho(n)(d)\ne\top\}.
\end{equation}
%\mtodo{Another change was that Ondrej defined $\backEq$ as $\lambda n.\{d\mid\rho(n)(d)=\top\}$
%and that he defined $\backEq$ related to the equivalence transformation.}
%\otodo{I don't understand this comment. What does it mean?}

In the correlated-calls transformation lattice $\lcc$, a map that maps any receiver
to the empty set of possible types means that the corresponding data flow path is
infeasible. Therefore, a result $\rho=\resultIDE(\transCC _S(P))$ of the correlated-calls IDE analysis is
converted to an IFDS result as follows:
\begin{equation}\label{eq:transCcDef}
    \backCC(\rho) = \lambda n.\{d\mid\forall r\in S\,.\,\rho(n)(d)(r)\neq\top_T\}.
\end{equation}
\otodo{In Equation (5), I changed $\rho(n)(d)$ to $\rho(n)(d)(r)$, because I think
    the original was incorrect. Marianna, please check that this correction is correct.}

@@

@@

\subsection{Efficiency}
\commentout{
\otodo{Sagiv et al. define a notion of an ``efficient'' implementation of micro-functions.
    If the micro-functions are ``efficient'', then the asymptotic complexity bounds proven by
    Sagiv hold. Our implementation is ``efficient'' if we assume that the number of correlated
    receivers is a constant independent of the size of the program. That seems a stretch. If
    it's linear in the size of the program, then we would need to add a factor to their complexity
    bounds. Their bound is $O(ED^3)$, while ours would be $O(ED^3R)$. But then we can't directly use their complexity proof; we would have to adapt it.
    I'm leaning towards leaving out any mention of ``efficient'' implementation.}
}

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The complexity proof for the IDE algorithm requires the implementation of the micro-functions
to be \textit{efficient} according to the following criteria:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
We prove that the micro-functions for the correlated-call analysis satisfy these
criteria if we consider the number of correlated-call receivers $R$ and the
number of run-time types $T$ constant
(i.e. the operations on micro-functions are allowed to use time that is $O(RT)$,
but constant with respect to $E$ and $D$).

\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient if the number of
  correlated-call receivers $R$ and the number of run-time types $T$ are considered constant.
\end{restatable}

From this lemma, we conclude that the correlated-calls analysis runs in time
$O(ED^3RT)$. In other words, the asymptotic cost of the added precision of
the correlated-calls analysis is increased by a factor of $O(RT)$ compared
to the original IFDS analysis.
